\documentclass[12pt]{article}
\usepackage{parskip}
\usepackage{hhline}
\begin{document}
\section{Student Robotics Competition 2014}

\subsection{Introduction}

Welcome to the competition \textbf{SCHOOL_LONG_NAME}! Throughout the
competition we will refer to your team by its three letter acronym
(\textbf{TLA}). For your team your TLA is \textbf{SCHOOL_TLA}.

This document contains a lot of helpful information about the competition.
We've included a schedule, as well as information on the structure of the
matches. We've also included some rules for the venue and a floor layout so
that you know where everything is.

\subsection{Pits and floor plan}

Each team has a pit, and we've marked yours on this diagram in red:

TODO: diagram

On the floor plan you'll also see the ``power tools area''. This is the only
place in the competition venue that you can use power tools.

There are two lifts in the venue. We've reserved one of them for teams that are
coming down from the second floor to their matches. Please use the other lift
at all times unless you are going to a match.

\subsection{Day Schedule}

This is the schedule for the two days of the competition.

\begin{center}
    \subsubsection{26/04/2014: Day 1}

    \begin{tabular}{|c|l|}
        \hline
        Time & Activity \\ \hline
        9:00 & Doors open \\ \hline
        9:30 & Introduction and Safety briefing \\ \hline
        9:45 & Tinkering time \\ \hline
        12:15 & Lunch and Tinkering time \\ \hline
        13:00 & League matches \\ \hline
        17:30 & End of day \\ \hline
    \end{tabular}

    \subsubsection{27/04/2014: Day 2}

    \begin{tabular}{|c|l|}
        \hline
        Time & Activity \\ \hline
        9:00 & Doors open \\ \hline
        9:30 & League matches \\ \hline
        12:15 & Lunch \\ \hline
        13:15 & League matches \\ \hline
        15:00 & Knockout matches \\ \hline
        17:00 & End of Knockout matches \\ \hline
        17:15 & Prize Ceremony \\ \hline
        18:00 & End of day \\ \hline
    \end{tabular}
\end{center}

\subsection{League Matches}

As per the rules, we are running the league matches to seed the knock out
round. Each league match has four teams. The winner of each league match wins 4
league points. The first runner up wins 3 league points. The second runner up
wins 2 league points. The loser of the match wins 1 league point. In the case
of a draw between any of these positions we average the league points across
teams.

Please ensure you are at any league match you are in precisely at the time
indicated. \textbf{We will not delay matches for teams that are not present.}.
Teams that do not show up to a match will get 0 league points.


There are 216 league matches this year, 108 in each arena. We have paired the
matches, so that the two arenas are always in sync. We have given the schedule
for the league matches below. Any matches containing your team have been
\textbf{emboldended}. CN means that your robot is in corner n. For example C0
means that your robot is in corner 0.


\begin{center}
    Day 1 league matches
    \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
        \hline
        \multicolumn{1}{|c|}{} & \multicolumn{4}{|c|}{Arena 0} & \multicolumn{4}{|c|}{Arena 1} \\ \hline
        Time &
 \multicolumn{1}{|c|}{C0}  &
 \multicolumn{1}{|c|}{C1}  &
 \multicolumn{1}{|c|}{C2}  &
 \multicolumn{1}{|c|}{C3}  &
 \multicolumn{1}{|c|}{C0}  &
 \multicolumn{1}{|c|}{C1}  &
 \multicolumn{1}{|c|}{C2}  &
 \multicolumn{1}{|c|}{C3} \\ \hhline{|=|=|=|=|=|=|=|=|=|}
        9:00 & EMM & SWI & EMM & SWI & EMM & SWI & EMM & SWI \\ \hline
    \end{tabular}
\end{center}

Day 2 league matches

\subsection{Knockout Matches}

Every team will take part in the knock out matches this year. In the first
round of the knock-out matches, both arenas will run matches. In all later
rounds of the knock-out matches \textbf{only Arena 0 will be used}.

The first round of the knock outs will be scheduled as follows (SN represents
seed position N from the league). \textbf{Note: displays around the venue will
show who is in which knock out matches as that data becomes available}


\begin{center}
    \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
        \hline
        \multicolumn{1}{|c|}{} & \multicolumn{4}{|c|}{Arena 0} & \multicolumn{4}{|c|}{Arena 1} \\ \hline
        Time &
 \multicolumn{1}{|c|}{C0}  &
 \multicolumn{1}{|c|}{C1}  &
 \multicolumn{1}{|c|}{C2}  &
 \multicolumn{1}{|c|}{C3}  &
 \multicolumn{1}{|c|}{C0}  &
 \multicolumn{1}{|c|}{C1}  &
 \multicolumn{1}{|c|}{C2}  &
 \multicolumn{1}{|c|}{C3} \\ \hhline{|=|=|=|=|=|=|=|=|=|}
 15:00 & S0  & S16 & S32 & S48 & S8  & S24 & S40 & - \\ \hline
 15:05 & S4  & S20 & S36 & S52 & S12 & S28 & S44 & - \\ \hline
 15:10 & S2  & S18 & S34 & S50 & S10 & S26 & S42 & - \\ \hline
 15:15 & S6  & S22 & S38 & -   & S14 & S30 & S46 & - \\ \hline
 15:20 & S15 & S31 & S47 & -   & S7  & S23 & S39 & - \\ \hline
 15:25 & S11 & S27 & S43 & -   & S3  & S19 & S35 & S51 \\ \hline
 15:30 & S13 & S29 & S45 & -   & S5  & S21 & S37 & S53 \\ \hline
 15:35 & S9  & S25 & S41 & -   & S1  & S17 & S33 & S49 \\ \hline
    \end{tabular}
\end{center}
\end{document}
